The hedging hyperprior for the normal distribution: unknown mean, unknown precision

### 2024-06-25 text/23/normal-hedging-hyperprior-part-1.Rmd
Updated 2022 files, part 2

Assume that $\tau$ is known and equal to $\tau_F$. Other cases with [mean known and precision unknown][sim2] and with [both mean and precision unknown][sim3] appear on different web pages.

[sim2]: http://new.pmean.com/normal-hedging-hyperprior-part2
[sim3]: http://new.pmean.com/normal-hedging-hyperprior-part3

>>>>

Assume that $\tau$ is known and equal to $\tau_F$. Other cases with [mean known and precision unknown][sim4] and with [both mean and precision unknown][sim5] appear on different web pages.

[sim4]: http://new.pmean.com/normal-hedging-hyperprior-part2
[sim5]: http://new.pmean.com/normal-hedging-hyperprior-part3

### 2024-06-25 text/23/normal-hedging-hyperprior-part-2.Rmd
Updated 2022 files, part 2

Consider a Bayesian analysis of an outcome variable that has a normal distribution with known mean and unknown precision. Assume that both the mean and the precision of the normal distribution are unknown. Other cases with [mean unknown and precision known][sim1] and with [both mean and precision unknown][sim3] appear on a different web pages.

[sim1]: http://new.pmean.com/normal-hedging-hyperprior-part1
[sim3]: http://new.pmean.com/normal-hedging-hyperprior-part3

>>>>

Consider a Bayesian analysis of an outcome variable that has a normal distribution with known mean and unknown precision. Assume that both the mean and the precision of the normal distribution are unknown. Other cases with [mean unknown and precision known][sim3] and with [both mean and precision unknown][sim5] appear on a different web pages.

[sim3]: http://new.pmean.com/normal-hedging-hyperprior-part1
[sim5]: http://new.pmean.com/normal-hedging-hyperprior-part3

### 2024-06-25 text/23/normal-hedging-hyperprior-part-3.Rmd
Updated 2022 files, part 2

Assume that both the mean and the precision of the normal distribution are unknown. Earlier cases with [mean unknown and precision known][sim1] and with [mean known and precision unknown][sim2] appear on a different web pages.

[sim1]: http://new.pmean.com/normal-hedging-hyperprior-part1
[sim2]: http://new.pmean.com/normal-hedging-hyperprior-part2

>>>>

Assume that both the mean and the precision of the normal distribution are unknown. Other cases with [mean unknown and precision known][sim3] and with [mean known and precision unknown][sim4] appear on a different web pages.

[sim3]: http://new.pmean.com/normal-hedging-hyperprior-part1
[sim4]: http://new.pmean.com/normal-hedging-hyperprior-part2
